---
name: Jacob T. Wittman
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA, MSc
position: PhD Student
address: 1980 Folwell Avenue, St. Paul, MN
phone: 319 651 9490
email: wittja01@gmail.com
github: wittja01
linkedin: wittja01
twitter: wittja01
headcolor: 414141
fontsize: 30pt
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse)
pacman::p_load(vitae)
pacman::p_load(lubridate)
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include = FALSE}
# Instructions for Education section
# If you want to add more than one bullet point of detail, it looks like you
# need to copy the entire tribble line verbatim and add another detail at the 
# end of the new line

# Things to add
  # - ESA
  # - If funded, Farm Bill trapping grant

# Adjusts to .tex
  # - Add `\\` (without `) after each \detaileditem full entry but only if they DON'T have a \empty preceeding them to fix the spacing issues
```



# Education
```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD Entomology, Concentration: Forest Entomology, Minor: Biostatistics", "University of Minnesota", "St. Paul, MN", "Sept. 2018 - 2022 (anticipated)", "Dissertation Topic: Emerald ash borer biocontrol modeling \n",
  
  "MSc Entomology, Concetration: Forest Entomology", "University of Minnesota", "St. Paul, MN", "Jun. 2016 - Sept. 2018", "GPA of 4.00",
  "MSc Entomology, Concetration: Forest Entomology", "University of Minnesota", "St. Paul, MN", "Jun. 2016 - Sept. 2018", "Thesis Title: Effects of host type and food deprivation on the movement behavior of late-instar larvae of gypsy moth Lymantria dispar (Lepidoptera: Erebidae)",
  
  "Teaching License in Secondary Education Biology", "Luther College", "Decorah, IA", "Sept. 2012 - Dec. 2013", "GPA of 4.00",
  "BA in Biology & Environmental Studies", "Luther College", "Decorah, IA", "Sept. 2008 - May 2012", "GPA of 3.68"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Publications

```{r pubs}
bibliography_entries("bibs/publications.bib") %>%
  filter(bibtype == "Article") %>% 
  arrange(desc(year), desc(`mendeley-tags`))
  
```

# Invited Presentations
  
  1. Wittman, JT, RA Nicoll, SW Myers, PH Chaloux, and BH Aukema (2019). _What You Eat Affects How You Move: Links Between Caterpillar Behavior and Gypsy Moth Management._ Oral presentation at the Annual Gypsy Moth Review, November 5 - 7, Seattle, WA.
  2. Wittman, JT, PH Chaloux, D Lance, SW Myers, and BH Aukema (2016). _I Would Walk 500 Miles: Orientation and Movement Potential of Gypsy Moth Larvae in a Simulated Lumber Yard._ Oral presentation at the Annual Gypsy Moth Review, October 25 – 27, Columbus, OH.

# Contributed Presentations

  1. Wittman, JT (2019). _Replicability and open science in entomology._ Oral presentation given at the Department of Entomology, University of Minnesota, October 22, St. Paul, MN.
  2. Wittman, JT, JJ Duan, RC Venette, and BH Aukema (2019). _Effect of cooling rate on survival of Spathius galinae when exposed to sub-zero temperatures._ Oral presentation at the North Central Forest Pest Workshop, September 23 - 26, Lisle, IL.
  3. Wittman, JT, and BH Aukema (2018). _Effects of host foliage on the movement behavior of larvae of gypsy moth (Lymantria dispar)._ Oral presentation at the Entomological Society of America, Annual Meeting, November 11 – 14, Vancouver, British Columbia, Canada.
  4. Wittman, JT, PH Chaloux, SW Myers, and BH Aukema (2018). _Keeping gypsy moth where they are: Investigating how far gypsy moth larvae can move._ Oral presentation at the Western Forest Insect Work Conference, March 26 - 29, Denver, CO.
  5. Wittman, JT, PH Chaloux, SW Myers, and BH Aukema (2018). _Developing science to support practice: Determining distances required to protect log decks from wandering gypsy moth larvae._ Poster presentation at the USDA Interagency Forum on Invasive Species, January 9 – 12, Annapolis, MD.
  6. Wittman, JT, SW Myers, PH Chaloux, and BH Aukema (2017). _Evaluating gypsy moth (Lymantria dispar) larval movement potential and effective barriers limiting their movement._ Oral presentation at the Entomological Society of America, Annual Meeting, November 5 – 8, Denver, CO.
  7. Wittman, JT, SW Myers, PH Chaloux, and BH Aukema (2017). _Supporting policy with science: Are buffer zones around wood products effective at preventing the spread of gypsy moth (Lymantria dispar)._ Oral presentation at the International Union of Forest Research Organizations - Forest Insects and Pathogens in a Changing Environment: Ecology, Monitoring, and Genetics, September 11 – 15, Thessaloniki, Greece.
  8. Wittman, JT, PH Chaloux, D Lance, SW Myers, and BH Aukema (2016). _Evaluating the effectiveness of buffer zone practices in preventing the spread of gypsy moth (Lymantria dispar)._ Oral presentation at the Gypsy Moth Program Advisory Committee Meeting, November 22, St. Paul, MN.
  9. Nicoll, RA, JT Wittman, SW Myers, D Lance, and BH Aukema (2016). _Do buffer zones prevent the spread of gypsy moth (_Lymantria dispar_) larvae?_ Poster presentation at the Upper Midwest Invasive Species Conference, October 16-19, La Crosse, WI.
  10. Wittman, J., E Stivers, and KJ Larsen (2016). _Bees, Butterflies and Beetles: A Comparison of Remnant and Planted Prairies in Northeast Iowa._ Oral presentation at the Day of Insects, April 9, Ames, IA.
  11. Stivers, E, JT Wittman, and KJ Larsen (2015). _A comparison of adult butterfly communities on remnant and planted prairies in Northeast Iowa._ Poster presentation at Entomological Society of America, 63rd Annual Meeting. November 14 – 18, Minneapolis, NM.
  12. Wittman, JT, A Weckwerth, and J Enos-Berlage (2012). _Exploring the Dry Run Creek Watershed: Molecules, Microbes, and Macroinvertebrates._ Poster presentation at the Iowa Water Conference. March.

# Teaching Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Guest Lecturer", "University of Minnesota", "St. Paul, MN", "Sept. 2019", "Forest Entomology (ENT 4251)",
  
  "Teaching Assistant", "University of Minnesota", "St. Paul, MN", "Sept. 2018 - Dec. 2018", "Insect Biology (ENT 1005)",
  
  "Science Teacher", "DREAM Technical Academy", "Willmar, MN", "Jun. 2014 - Jun. 2016", "Grades 7 - 12",
  "Long-Term Substitute - Biology", "Faribault High School", "Faribault, MN", "Feb. 2014 - Apr. 2014", "Biology (Grade 11)",
   "Long-Term Substitute - Biology", "Faribault High School", "Faribault, MN", "Feb. 2014 - Apr. 2014", "Integrated Life Science (Grade 9)",
  "Tutor", "Huntington Learning Center", "Plymouth, MN", "Oct. 2013 - Aug. 2014", "Science (Grades 6 - 12)",
  "Tutor", "Huntington Learning Center", "Plymouth, MN", "Oct. 2013 - Aug. 2014", "Math (Grades 6 - 12)",
  "Tutor", "Huntington Learning Center", "Plymouth, MN", "Oct. 2013 - Aug. 2014", "ACT (Grades 11 - 12)",
  "Student Teacher", "Edina High School", "Edina, MN", "Oct. 2013 - Dec. 2013", "Biology (Grade 11)",
  "Student Teacher", "Edina High School", "Edina, MN", "Oct. 2013 - Dec. 2013", "AP Biology (Grade 12)",
  "Student Teacher", "Stillwater Junior High", "Stillwater, MN", "Aug. 2013 - Oct. 2013", "Life Sciences (Grade 7)"
) %>% 
  detailed_entries(role, dates, company, loc, details)
```


# Software 

1. Wittman, JT and BH Aukema (2019). _servosphereR: Analyze data generated from SynTech Servosphere trials_. R software package. https://cran.r-project.org/web/packages/servosphereR/. 


# Grants, Fellowships, & Honors

```{r}
tribble(
  ~ scholarship, ~ from, ~ city, ~ year, ~ amount,
  "Council of Graduate Students Travel Grant", "University of Minnesota", "St. Paul, MN", "2019", "$205",
  
  "Chiang Travel Award", "Department of Entomology, University of Minnesota", "St. Paul, MN", "2018", "$200",
  
  "Characterizing dispersal of larval gypsy moth to improve quarantine regulations", "Minnesota Invasive Terrestrial Plant and Pest Center", "St. Paul, MN", "2018", "$35,000",
  
  "Chiang Travel Award", "Department of Entomology, University of Minnesota", "St. Paul, MN", "2017", "$200",
  
  "McLaughlin Gormley King (MGK) Fellowship", "Department of Entomology, University of Minnesota", "St. Paul, MN", "2016 - 2017", "$42,600",
  
  "Howard Hughes Medical Institute Teacher Scientist Fellowship", "Luther College", "Decorah, IA", "2012 - 2013", "$12,500"
) %>%
  detailed_entries(from, year, scholarship, city, amount)
```


# Service
```{r}
tribble(
  ~ position, ~ group, ~ year, ~ city,
  "President", "Frenatae (Entomology graduate student association, University of Minnesota)", "2019 - present", "St. Paul, MN",
  
  "Student Presentation Organizer", "North Central Forest Pest Workshop", "2019", "Lisle, IL", 
  
  "Volunteer", "Reproducible Research with R Workshop", "2019", "St. Paul, MN", 
  
  "Grant Reviewer", "Council of Graduate Students, University of Minnesota", "2019", "St. Paul, MN", 
  
  "Treasurer", "Frenatae (Entomology graduate student association, University of Minnesota)", "2018 - 2019", "St. Paul, MN", 
  
  "Insect Education Outreach Coordinator", "Frenatae (Entomology graduate student association, University of Minnesota)", "2017 - 2018", "St. Paul, MN", 
  
  "Council of Graduate Students Representative", "Frenatae (Entomology graduate student association, University of Minnesota)", "2016 - 2017", "St. Paul, MN", 
) %>% 
  detailed_entries(group, year, position, city)
```

# Peer Review Service 
```{r peer_review_notes, include = FALSE}
# To add more entries for journals or grants enter empty quotes for the ~type variable
```
```{r}
tribble(
  ~ type, ~ specifics, ~ year,
  "Journals", "Journal of Economic Entomology", "2019",
  
  "Grants", "Council of Graduate Students Travel and Professional Development Grants", "2019" 
) %>% 
  brief_entries(specifics, type, year)
```