---
name: Jacob Timothy Wittman
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BSc, MSc
position: PhD Student
address: 1980 Folwell Avenue, St. Paul, MN
phone: 319 651 9490
email: wittja01@gmail.com
github: wittja01
linkedin: wittja01
twitter: wittja01
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse)
pacman::p_load(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include = FALSE}
# Instructions for Education section
# If you want to add more than one bullet point of detail, it looks like you
# need to copy the entire tribble line verbatim and add another detail at the 
# end of the new line
```


# Education
```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD Entomology, Concetration: Forest Entomology, Minor: Biostatistics", "University of Minnesota", "St. Paul, MN", "Sept. 2018 - 2022 (anticipated)", "Dissertation Topic: Emerald ash borer biocontrol modeling",
  "MSc Entomology, Concetration: Forest Entomology", "University of Minnesota", "St. Paul, MN", "Jun. 2016 - Sept. 2018", "GPA of 4.00",
  "MSc Entomology, Concetration: Forest Entomology", "University of Minnesota", "St. Paul, MN", "Jun. 2016 - Sept. 2018", "Thesis Title: Effects of host type and food deprivation on the movement behavior of late-instar larvae of gypsy moth Lymantria dispar (Lepidoptera: Erebidae)",
  "Teaching License in Secondary Education Biology", "Luther College", "Decorah, IA", "Sept. 2012 - Dec. 2013", "GPA of 4.00",
  "BA in Biology & Environmental Studies", "Luther College", "Decorah, IA", "Sept. 2008 - May 2012", "GPA of 3.68"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Teaching Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Advanced statistical modelling (ETC3580)",
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Business forecasting (ETF3231/ETF5231)",
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Mathematics for business (ETF2700)",
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Data modelling and computing (ETC1010)",
  "Research Assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Supervisors include Rob Hyndman, Dianne Cook, and George Athanasopoulos.",
  "Research Assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Consulting projects with DiabetesLab, Tennis Australia, Monash University and Huawei.",
  "Research Assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Contributed to the development of numerous open source R packages.",
  "Volunteer", "Rotaract", "Monash, Australia", "Feb. 2013 - Nov. 2016", "Development and maintenance of club website and online services.",
  "Volunteer", "Rotaract", "Monash, Australia", "Feb. 2013 - Nov. 2016", "Organising and hosting fundraisers.",
  "Student Ambassador", "Google", "Sydney, Australia", "Feb. 2015 - Nov. 2015", "Supported Google's presence on campus with events and media.",
  "Data Mining (Internship)", "iSelect", "Cheltenham, Australia", "Feb. 2015 - Mar. 2015", "Improved business data and issue reporting with interactive visualisations, and model-based anomaly detection.",
  "Fresh Produce", "Coles", "Rowville, Australia", "Oct. 2010 - Nov. 2015", "Food preparation & display, first aid, staff training and customer assistance."
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

\newpage



```{r pubs}
bibliography_entries("bibs/publications.bib", 
                     title = "Publications") %>%
  filter(bibtype == "Article") %>% 
  arrange(desc(year), author)
```

## Presentations

  * __Wittman, JT__, and BH Aukema (2018). _Effects of host foliage on the movement behavior of larvae of gypsy moth (Lymantria dispar)._ Oral presentation at the Entomological Society of America, Annual Meeting, November 11 – 14, Vancouver, British Columbia, Canada.
  * __Wittman, JT__, PH Chaloux, SW Myers, and BH Aukema (2018). _Keeping gypsy moth where they are: Investigating how far gypsy moth larvae can move._ Oral presentation at the Western Forest Insect Work Conference, March 26 - 29, Denver, CO.
  * __Wittman, JT__, PH Chaloux, SW Myers, and BH Aukema (2018). _Developing science to support practice: Determining distances required to protect log decks from wandering gypsy moth larvae._ Poster presentation at the USDA Interagency Forum on Invasive Species, January 9 – 12, Annapolis, MD.
  * __Wittman, JT__, SW Myers, PH Chaloux, and BH Aukema (2017). _Evaluating gypsy moth (Lymantria dispar) larval movement potential and effective barriers limiting their movement._ Oral presentation at the Entomological Society of America, Annual Meeting, November 5 – 8, Denver, CO.
  * __Wittman, JT__, SW Myers, PH Chaloux, and BH Aukema (2017). _Supporting policy with science: Are buffer zones around wood products effective at preventing the spread of gypsy moth (Lymantria dispar)._ Oral presentation at the International Union of Forest Research Organizations - Forest Insects and Pathogens in a Changing Environment: Ecology, Monitoring, and Genetics, September 11 – 15, Thessaloniki, Greece.
  * __Wittman, JT__, PH Chaloux, D Lance, SW Myers, and BH Aukema (2016). _Evaluating the effectiveness of buffer zone practices in preventing the spread of gypsy moth (Lymantria dispar)._ Oral presentation at the Gypsy Moth Program Advisory Committee Meeting, November 22, St. Paul, MN.
  * __Wittman, JT__, PH Chaloux, D Lance, SW Myers, and BH Aukema (2016). _I Would Walk 500 Miles: Orientation and Movement Potential of Gypsy Moth Larvae in a Simulated Lumber Yard._ Oral presentation at the Annual Gypsy Moth Review, October 25 – 27, Columbus, OH.
  * Nicoll, RA, __JT Wittman__, SW Myers, D Lance, and BH Aukema (2016). _Do buffer zones prevent the spread of gypsy moth (_Lymantria dispar_) larvae?_ Poster presentation at the Upper Midwest Invasive Species Conference, October 16-19, La Crosse, WI.
  * __Wittman, J.__, E Stivers, and KJ Larsen (2016). _Bees, Butterflies and Beetles: A Comparison of Remnant and Planted Prairies in Northeast Iowa._ Oral presentation at the Day of Insects, April 9, Ames, IA.
  * Stivers, E, __JT Wittman__, and KJ Larsen (2015). _A comparison of adult butterfly communities on remnant and planted prairies in Northeast Iowa._ Poster presentation at Entomological Society of America, 63rd Annual Meeting. November 14 – 18, Minneapolis, MN.
  * __Wittman, JT__, A Weckwerth, and J Enos-Berlage (2012). _Exploring the Dry Run Creek Watershed: Molecules, Microbes, and Macroinvertebrates._ Poster presentation at the Iowa Water Conference. March.

# Awards & Achievements
## Awards
```{r}
tribble(
  ~ award, ~ from, ~ year,
  "Commerce Dean's Honour", "Monash", "2017",
  "Commerce Dean's Commendation", "Monash", "2016",
  "Science Dean’s List", "Monash", "2014-2016",
  "International Institute of Forecasters Award", "IIF", "2014",
  "Rotary Youth Leadership Award", "Rotary", "2013"
) %>%
  brief_entries(award, year, from)
```

## Scholarships
```{r}
tribble(
  ~ scholarship, ~ from, ~ year,
  "Econometrics Honours Memorial Scholarship", "Monash", "2017",
  "Monash Community Leaders Scholarship", "Monash", "2015 & 2016",
  "Mitcham Rotary Scholarship", "Rotary", "2011 & 2012"
) %>%
  brief_entries(scholarship, year, from)
```


## Competitions
```{r}
tribble(
  ~ competition, ~ from, ~ year,
  "UseR! 2018 Datathon Champion", "UseR!", "2018",
  "RMIT SBITL Analytics Competition Champion", "RMIT", "2017",
  "RMIT SBITL Analytics Competition Champion", "RMIT", "2016"
) %>%
  brief_entries(competition, year, from)
```
