%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Jacob T. Wittman}{}

\position{PhD Student}
\address{1980 Folwell Avenue, St.~Paul, MN}

\mobile{319 651 9490}
\email{\href{mailto:wittja01@gmail.com}{\nolinkurl{wittja01@gmail.com}}}
\github{wittja01}
\linkedin{wittja01}
\twitter{wittja01}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{
\cventry{#1}{#3}{#4}{#2}{\ifx#5\empty\else{\begin{cvitems}#5\end{cvitems}}\fi}}
\def\detailedsection#1{\begin{cventries}#1\end{cventries}}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvhonor{}{#1}{#3}{#2}}
\def\briefsection#1{\begin{cvhonors}#1\end{cvhonors}}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


%%%% BIBLIOGRAPHY
% Bibliography formatting

\usepackage[sorting=ynt,citestyle=authoryear,bibstyle=authoryear-comp,defernumbers=true,maxnames=20,giveninits=true, bibencoding=utf8, terseinits=true, uniquename=init,dashed=false,doi=false,isbn=false,natbib=true,backend=biber]{biblatex}

\DeclareFieldFormat{url}{\url{#1}}
\DeclareFieldFormat[article]{pages}{#1}
\DeclareFieldFormat[inproceedings]{pages}{\lowercase{pp.}#1}
\DeclareFieldFormat[incollection]{pages}{\lowercase{pp.}#1}
\DeclareFieldFormat[article]{volume}{\mkbibbold{#1}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\DeclareFieldFormat[article]{title}{\MakeCapital{#1}}
\DeclareFieldFormat[article]{url}{}
\DeclareFieldFormat[inproceedings]{title}{#1}
\DeclareFieldFormat{shorthandwidth}{#1}
\DeclareFieldFormat{extradate}{}

% No dot before number of articles
\usepackage{xpatch}
\xpatchbibmacro{volume+number+eid}{\setunit*{\adddot}}{}{}{}

% Remove In: for an article.
\renewbibmacro{in:}{%
  \ifentrytype{article}{}{%
  \printtext{\bibstring{in}\intitlepunct}}}

%\makeatletter
%\DeclareDelimFormat[cbx@textcite]{nameyeardelim}{\addspace}
%\makeatother

\setlength{\bibitemsep}{1.8pt}
\setlength{\bibhang}{.9cm}
%\renewcommand{\bibfont}{\fontsize{12}{14}}

\renewcommand*{\bibitem}{\addtocounter{papers}{1}\item \mbox{}\hskip-0.9cm\hbox to 0.9cm{\hfill\arabic{papers}.~\,}}
\defbibenvironment{bibliography}
{\list{}
  {\setlength{\leftmargin}{\bibhang}%
   \setlength{\itemsep}{\bibitemsep}%
   \setlength{\parsep}{\bibparsep}}}
{\endlist}
{\bibitem}

\renewcommand{\bibfont}{\normalfont\fontsize{10}{12.4}\selectfont}
% Counters for keeping track of papers
\newcounter{papers}

\DeclareSortingScheme{ty}{
  \sort{
    \field{title}
  }
  \sort{
    \field{year}
  }
}
\DeclareBibliographyCategory{bib}
\bibliography{bibs/publications.bib}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {September, 2019}
  {Jacob T. Wittman~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\detailedsection{\detaileditem
{PhD Entomology, Concetration: Forest Entomology, Minor: Biostatistics}
{Sept. 2018 - 2022 (anticipated)}
{University of Minnesota}
{St. Paul, MN}
{\item{Dissertation Topic: Emerald ash borer biocontrol modeling}}\detaileditem
{MSc Entomology, Concetration: Forest Entomology}
{Jun. 2016 - Sept. 2018}
{University of Minnesota}
{St. Paul, MN}
{\item{GPA of 4.00}\item{Thesis Title: Effects of host type and food deprivation on the movement behavior of late-instar larvae of gypsy moth Lymantria dispar (Lepidoptera: Erebidae)}}\detaileditem
{Teaching License in Secondary Education Biology}
{Sept. 2012 - Dec. 2013}
{Luther College}
{Decorah, IA}
{\item{GPA of 4.00}}\detaileditem
{BA in Biology \& Environmental Studies}
{Sept. 2008 - May 2012}
{Luther College}
{Decorah, IA}
{\item{GPA of 3.68}}}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\detailedsection{\detaileditem
{Guest Lecturer}
{Sept. 2019}
{University of Minnesota}
{St. Paul, MN}
{\item{Forest Entomology (ENT 4251)}}\detaileditem
{Teaching Assistant}
{Sept. 2018 - Dec. 2018}
{University of Minnesota}
{St. Paul, MN}
{\item{Insect Biology (ENT 1005)}}\detaileditem
{Science Teacher}
{Jun. 2014 - Jun. 2016}
{DREAM Technical Academy}
{Willmar, MN}
{\item{Grades 7 - 12}}\detaileditem
{Long-Term Substitute - Biology}
{Feb. 2014 - Apr. 2014}
{Faribault High School}
{Faribault, MN}
{\item{Biology (Grade 11)}\item{Integrated Life Science (Grade 9)}}\detaileditem
{Tutor}
{Oct. 2013 - Aug. 2014}
{Huntington Learning Center}
{Plymouth, MN}
{\item{Science (Grades 6 - 12)}\item{Math (Grades 6 - 12)}\item{ACT (Grades 11 - 12)}}\detaileditem
{Student Teacher}
{Oct. 2013 - Dec. 2013}
{Edina High School}
{Edina, MN}
{\item{Biology (Grade 11)}\item{AP Biology (Grade 12)}}\detaileditem
{Student Teacher}
{Aug. 2013 - Oct. 2013}
{Stillwater Junior High}
{Stillwater, MN}
{\item{Life Sciences (Grade 7)}}}

\newpage

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\defbibheading{bib}{\subsection{}}
\addtocategory{bib}{Wittman2019,
Wittman2018,
Stivers2019,
Wittman2017,
Wittman2013}
\newrefcontext[sorting=ydnt]\setcounter{papers}{0}\pagebreak[3]
\printbibliography[category=bib,heading=bib]\setcounter{papers}{0}

\nocite{Wittman2019,
Wittman2018,
Stivers2019,
Wittman2017,
Wittman2013}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

Wittman, JT, JJ Duan, RC Venette, and BH Aukema (2019). \emph{Effect of
cooling rate on survival of \textbf{Spathius galinae} when exposed to
sub-zero temperatures.} Oral presentation at the North Central Forest
Pest Workshop, September 23 - 26, Lisle, Illinois. 1. Wittman, JT, and
BH Aukema (2018). \emph{Effects of host foliage on the movement behavior
of larvae of gypsy moth (Lymantria dispar).} Oral presentation at the
Entomological Society of America, Annual Meeting, November 11 -- 14,
Vancouver, British Columbia, Canada. 2. Wittman, JT, PH Chaloux, SW
Myers, and BH Aukema (2018). \emph{Keeping gypsy moth where they are:
Investigating how far gypsy moth larvae can move.} Oral presentation at
the Western Forest Insect Work Conference, March 26 - 29, Denver, CO. 3.
Wittman, JT, PH Chaloux, SW Myers, and BH Aukema (2018).
\emph{Developing science to support practice: Determining distances
required to protect log decks from wandering gypsy moth larvae.} Poster
presentation at the USDA Interagency Forum on Invasive Species, January
9 -- 12, Annapolis, MD. 4. Wittman, JT, SW Myers, PH Chaloux, and BH
Aukema (2017). \emph{Evaluating gypsy moth (Lymantria dispar) larval
movement potential and effective barriers limiting their movement.} Oral
presentation at the Entomological Society of America, Annual Meeting,
November 5 -- 8, Denver, CO. 5. Wittman, JT, SW Myers, PH Chaloux, and
BH Aukema (2017). \emph{Supporting policy with science: Are buffer zones
around wood products effective at preventing the spread of gypsy moth
(Lymantria dispar).} Oral presentation at the International Union of
Forest Research Organizations - Forest Insects and Pathogens in a
Changing Environment: Ecology, Monitoring, and Genetics, September 11 --
15, Thessaloniki, Greece. 6. Wittman, JT, PH Chaloux, D Lance, SW Myers,
and BH Aukema (2016). \emph{Evaluating the effectiveness of buffer zone
practices in preventing the spread of gypsy moth (Lymantria dispar).}
Oral presentation at the Gypsy Moth Program Advisory Committee Meeting,
November 22, St.~Paul, MN. 7. Wittman, JT, PH Chaloux, D Lance, SW
Myers, and BH Aukema (2016). \emph{I Would Walk 500 Miles: Orientation
and Movement Potential of Gypsy Moth Larvae in a Simulated Lumber Yard.}
Oral presentation at the Annual Gypsy Moth Review, October 25 -- 27,
Columbus, OH. 8. Nicoll, RA, JT Wittman, SW Myers, D Lance, and BH
Aukema (2016). \emph{Do buffer zones prevent the spread of gypsy moth
(\emph{Lymantria dispar}) larvae?} Poster presentation at the Upper
Midwest Invasive Species Conference, October 16-19, La Crosse, WI. 9.
Wittman, J., E Stivers, and KJ Larsen (2016). \emph{Bees, Butterflies
and Beetles: A Comparison of Remnant and Planted Prairies in Northeast
Iowa.} Oral presentation at the Day of Insects, April 9, Ames, IA. 10.
Stivers, E, JT Wittman, and KJ Larsen (2015). \emph{A comparison of
adult butterfly communities on remnant and planted prairies in Northeast
Iowa.} Poster presentation at Entomological Society of America, 63rd
Annual Meeting. November 14 -- 18, Minneapolis, MN. 11. Wittman, JT, A
Weckwerth, and J Enos-Berlage (2012). \emph{Exploring the Dry Run Creek
Watershed: Molecules, Microbes, and Macroinvertebrates.} Poster
presentation at the Iowa Water Conference. March.

\hypertarget{software}{%
\section{Software}\label{software}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Wittman, JT and BH Aukema (2019). \emph{servosphereR: Analyze data
  generated from SynTech Servosphere trials}. R software package.
  \url{https://cran.r-project.org/web/packages/servosphereR/}.
\end{enumerate}

\newpage

\hypertarget{grants}{%
\section{Grants}\label{grants}}

\detailedsection{\detaileditem
{Minnesota Invasive Terrestrial Plant and Pest Center}
{2018}
{Characterizing dispersal of larval gypsy moth to improve quarantine regulations}
{St. Paul, MN}
{\item{\$35,000}}}

\hypertarget{fellowships-honors}{%
\section{Fellowships \& Honors}\label{fellowships-honors}}

\detailedsection{\detaileditem
{Department of Entomology, University of Minnesota}
{2018}
{Chiang Travel Award}
{St. Paul, MN}
{\item{\$200}}\detaileditem
{Department of Entomology, University of Minnesota}
{2017}
{Chiang Travel Award}
{St. Paul, MN}
{\item{\$200}}\detaileditem
{Department of Entomology, University of Minnesota}
{2016 - 2017}
{McLaughlin Gormley King (MGK) Fellowship}
{St. Paul, MN}
{\item{\$42,600}}\detaileditem
{Luther College}
{2012 - 2013}
{Howard Hughes Medical Institute Teacher Scientist Fellowship}
{Decorah, IA}
{\item{\$12,500}}}

\hypertarget{service}{%
\section{Service}\label{service}}

\detailedsection{\detaileditem
{Reproducible Research with R Workshop}
{2019}
{Volunteer}
{St. Paul, MN}
{\empty}\detaileditem
{Council of Graduate Students, University of Minnesota}
{2019}
{Grant Reviewer}
{St. Paul, MN}
{\empty}\detaileditem
{Frenatae (Entomology graduate student association, University of Minnesota)}
{2019 - present}
{President}
{St. Paul, MN}
{\empty}\detaileditem
{Frenatae (Entomology graduate student association, University of Minnesota)}
{2018 - 2019}
{Treasurer}
{St. Paul, MN}
{\empty}\detaileditem
{Frenatae (Entomology graduate student association, University of Minnesota)}
{2017 - 2018}
{Insect Education Outreach Coordinator}
{St. Paul, MN}
{\empty}\detaileditem
{Frenatae (Entomology graduate student association, University of Minnesota)}
{2016 - 2017}
{Council of Graduate Students Representative}
{St. Paul, MN}
{\empty}}

\end{document}
